A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-05-29 sections/Metatheory.tex
Abella

% ---------------------------------------------
\subsection{Abella and Proof Statistics}
\bruno{Comment about correspondence between small and big step should
  probably come here.}

\jimmy{Discuss briefly on the difference of encodings in the script and this paper.}
While the algorithmic rules are in a small-step style,
the proof script rewrites them into a big-step style,
where inductions are more strightforward to handle.
In addition, we do prove the equivalence of the two representations.

@@

\paragraph{Statistics of the Proof}
The proof script consists of 7683 lines of Abella code with a total of
51 definitions and 567 theorems.
Figure~\ref{fig:proof_statistics} briefly summarizes the contents of each file.
The files are linearly dependent due to the limitation of Abella.

>>>>

% ---------------------------------------------
\subsection{Abella and Proof Statistics}

@@

While the algorithmic rules are in a small-step style,
the proof script rewrites them into a big-step style,
where inductions are easier to handle.
In addition, we do prove the equivalence of the two representations.

\paragraph{Statistics of the Proof}
The proof script consists of 7683 lines of Abella code with a total of
51 definitions and 567 theorems.
Figure~\ref{fig:proof_statistics} briefly summarizes the contents of each file.
The files are linearly dependent due to limitations of Abella.
